Digital Analysis of Paintings

### 2014-04-26 paper.tex
Add another paper.

\subsection{Difference Visualisation}
% Paper 6

@@

This aspect is lost in the digitisation of the painting; but there are still
ways of analysing the texture of the image.

>>>>

\subsection{Difference Visualisation}
% Paper 6
Another approach to colour is to visualise the difference between two or more
different images, this is particularly of use for comparing different versions
of the same image - the original to a famous forgery, for example.

Image fusion is the process of combining two different images and has recently
been applied to artwork\cite{blazek13image}. In this research, a technique for
showing the differences between two or more images which can show positive,
negative and zero difference between the images, whilst maintaining regions of
interest between the two images.

The method for doing this uses the CIELAB colour space, which maps more
faithfully to human vision than other colour spaces. However, because of the
limitations displaying the images, they are converted to \gls{HSV} before they
are displayed.

A hue for both the positive and negative difference values is selected by the
user as a vector, then the difference in the \gls{HSV} saturation of the two
images is then computed into CIELAB, where it is an angle between the
aforementioned colour vector.

Finally this is converted into \gls{HSV}, where the Hue represents the sign of
the computed image, the saturation the absolute distance and the value the
average value of intensities of the compared image at that pixel.

The authors claim this fusion improves the comprehension of the difference
visualisation of images and that it makes identifying regions of interest
faster and more precise, but provide no experimental results to prove this
other than the fused image result of four different copies of the same artwork.

This does keep the original image intact (albeit in grayscale with differences
highlighted).

This does only provide visualisation rather than analysis, but could potential
be used as part of a larger system to build more complex analysis techniques.
This might be especially useful to pick up difference between an original and a
derivative work or forgery.

At current, the images must be aligned and scaled manually, but this process
could be automated trivially.

@@

This aspect is lost in the digitisation of the painting; but there are still
ways of analysing the texture of the image by analysing the colour of the
image. Quite often, this is as effective on a one dimensional colour space as
it is on a three dimensional one.

Filters can be passed over an image to gather basic information such as
direction of lines within the paintings. More complex techniques for analysing
texture involve using wavelets and considering nearby pixels.
